---
---

```{r}
library(dplyr)
library(ggplot2)
```

```{r}
InverseLogit <- function(x){
  exp(x) / (exp(x) + 1)
}
```


```{r cache=TRUE}
load("disag.rda")
```

## No coefficients

```{r}
fitEOG_Intercept <- glm(data = dfEOG
                        , pct_glp ~ 1
                        , family = binomial)
summary(fitEOG_Intercept)

InverseLogit(coef(fitEOG_Intercept)[[1]])
```

## Univariate models

### AIG

We start by visualizing the relationship between AIG percent and GLP. We will note that there is a positive relationship between the two.

```{r}
pltAIG <- ggplot(dfEOG, aes(PctAIG, pct_glp)) + geom_point()
pltAIG
```

```{r}
fitEOG_AIG <- glm(data = dfEOG
                     , pct_glp ~ 1 + PctAIG
                     , family = binomial)
summary(fitEOG_AIG)

dfEOG$PredictAIG <- predict(fitEOG_AIG, type = "response")

pltAIG <- ggplot(dfEOG, aes(PctAIG, pct_glp)) + geom_point()
pltAIG <- pltAIG + geom_line(aes(PctAIG, PredictAIG), color = "red")
pltAIG
```

### Gender

```{r}
fitEOG_Gender <- glm(data = dfEOG
                     , pct_glp ~ 1 + PctFemale
                     , family = binomial)

summary(fitEOG_Gender)

dfEOG$PredictGender <- predict(fitEOG_Gender, type = "response")

InverseLogit(.01)

gonzo <- data.frame(PctFemale = seq(.01, .99, by = .01))
gonzo$Predict <- predict(fitEOG_Gender, newdata = gonzo)
gonzo$PredictResponse <- predict(fitEOG_Gender, newdata = gonzo, type = "response")

InverseLogit(coef(fitEOG_Gender)[[1]] + .01 * coef(fitEOG_Gender)[[2]])
```

```{r}
pltGender <- ggplot(dfEOG, aes(PctFemale, pct_glp)) + geom_point()
pltGender <- pltGender + geom_line(aes(PctFemale, PredictGender), color = "red")
pltGender

pltGender + scale_x_continuous(limits = c(0.4, 0.6))
```

### Grade

```{r}
fitEOG_Grade <- glm(data = dfEOG
                    , pct_glp ~ 1 + gradeFactor
                    , family = binomial)

summary(fitEOG_Grade)

pltGrade <- ggplot(dfEOG, aes(gradeFactor, pct_glp)) + geom_boxplot()
pltGrade
```

## Bivariate models

### AIG and Gender

As we would expect, inclusion of both variables improves the model. Note that the magnitude of the AIG parameter is higher than % female and the variance around the estimate is lower.

```{r}
fitEOG_AIG_Gender <- glm(data = dfEOG
                         , pct_glp ~ 1 + PctAIG + PctFemale
                         , family = binomial)

summary(fitEOG_AIG_Gender)
```

We wonder if there is a correlation between AIG and gender.

```{r}
fitAIG_Gender <- glm(data = dfEOG
                     , PctAIG ~ 1 + PctFemale
                     , family = binomial)
summary(fitAIG_Gender)

pltAIG_Gender <- ggplot(dfEOG, aes(PctAIG, PctFemale)) + geom_point(alpha = 0.02)
pltAIG_Gender
```

```{r}
fitEOG_AIG_Gender <- glm(data = dfEOG
                         , pct_glp ~ 1 + PctAIG + PctFemale
                         , family = binomial)

```



```{r}
fitEOG_AIG_GenderInteract <- glm(data = dfEOG
                                 , pct_glp ~ 1 + PctAIG:PctFemale
                                 , family = binomial)

summary(fitEOG_AIG_GenderInteract)
```

### Grade and gender