---
title: EDA Disag
---

```{r}
library(dplyr)
library(RSQLite)
library(ggplot2)
```

# Connect to SQLite

First, we'll fetch the data and pop it into a data frame.

```{r cache=TRUE}
con <- dbConnect(drv = SQLite(), dbname = "./cleaned/disag.db")
dbListTables(con)
dfDisag <- dbGetQuery(con, "SELECT * FROM disag")
```

# Very basic stuff

```{r}
knitr::kable(head(dfDisag))
```

```{r }
names(dfDisag)

lapply(dfDisag, class)
```

The class of some of the columns suggests that there are some inappropriate data types. `num_glp` for example smells numeric, but we're storing it as character. I'll go ahead and convert a few of those.

```{r cache=TRUE}
dfDisag <- dfDisag %>% 
  mutate(pct_glp = as.numeric(pct_glp)
         , num_glp = as.numeric(num_glp))
```

## Some denormalization

This will likely need to get moved out of EDA and into an earlier data processing step. I'm going to try and have a look at some of the denormalized data. I think School is the only such table. I'm not 100% clear on whether `grade_span` ought to be a property of the school or the result record.

```{r}
dfSchool <- dfDisag %>% 
  select(SchoolCode = school_code, SchoolName = name) %>% 
  unique()
```

```{r}
table(dfDisag$grade_span)

dfSchoolGradeSpan <- dfDisag %>% 
  select(SchoolCode = school_code, SchoolName = name, GradeSpan = grade_span) %>% 
  unique()

nrow(dfSchool) == nrow(dfSchoolGradeSpan)

dfMultiGradeSpan <- dfSchoolGradeSpan %>% 
  group_by(SchoolCode) %>% 
  summarise(NumRec = n()) %>% 
  filter(NumRec > 1)
```

OK, so there's a bunch of schools that have multiple grade spans.

## Category tables

The hierarchy of the categories isn't 100% clear to me. We'll have a look at some tables

```{r}
table(dfDisag$subject)
table(dfDisag$grade)
table(dfDisag$type)
table(dfDisag$subgroup)
```

### subgroup

* _AIG_ = *A*cademically and _I_ ntellecutally _G_ ifted
* _AMIN_ = _AM_erican _IN_dian
* _EDS_ = ???
* _LEP_ = ?? _E_ducation _P_lan ??
* _MIG_ = ???
* _SWD_ = ?? _S_tudents With Disability ??

## Basic numeric diagnostics

```{r}
hist(dfDisag$avg_score)
```

```{r}
hist(dfDisag$pct_glp)
```

```{r}
plt <- ggplot(dfDisag, aes(pct_glp, fill = school_year)) + geom_density(alpha = 0.6)
plt
```

```{r}
dfByYear <- dfDisag %>% 
  group_by(school_year) %>% 
  summarise(MedianGLP = median(pct_glp, na.rm = TRUE)
            , MeanGLP = mean(pct_glp, na.rm = TRUE))
```

We've got `num_tested` and `num_glp`. That suggests a poisson model where num_tested is an offset term. I'm still struggling with the observations by school. 

# Flotsam

http://www.educationnewyork.com/files/The%20importance%20of%20disaggregating_0.pdf 
http://edglossary.org/disaggregated-data/

What is this: http://www.ncpublicschools.org/accountability/reporting/datasets ?